No need to know: astrophysics-agnostic gravitational wave cosmology

### 2024-03-10 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[]{aastex631}
\usepackage{showyourwork}
\usepackage{macros}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{acro}

\DeclareAcronym{\ac{LVK}}{short=\ac{LVK}, long=LIGO Virgo KAGRA}
\DeclareAcronym{O5}{short=O5, long=the fifth LIGO Virgo KAGRA observing run}

@@

In other words, when using parametric models, $\frac{\diff N}{\diff t_{\det} \diff \theta_i} (\theta_i;\Lambda)$ in Equation~\ref{eq:inhomog-poisson} is calculated by evaluating a specific functional form described by a small set of hyper-parameters. 
With the GP approach, the hyper-parameters describing the mass distribution are the rate at each event-level posterior sample's source frame mass, and the rate at each found injection's source frame mass.
% The source frame mass is different for each possible value of \Ho{} and \Omm{}, so the hyper-parameters are defined in different locations for each draw from the hyper-posterior.
We therefore have $N_{\text{evs}}M + N_{\text{inj}}$ mass hyper-parameters, where $N_{\text{ev}}$ is the number of events, $M$ is the number of PE samples per event, and $N_{\text{inj}}$ is the number of injections used to calculate the selection function $\xi$.
We label these $\{\mathcal{R}_{ij},\mathcal{R}_k\}$, and our full set of hyper-parameters is $\Lambda=\{H_0, \Omega_M, \mathcal{R}_{ij},\mathcal{R}_k\}$. 
In this way, our GP-based mass distribution is similar to the autoregressive population models used in ~\citet{callister_parameter-free_2023}.
Indeed, an autoregressive model is a Gaussian process with a particular choice of kernel.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CE_GP.pdf}
    \caption{Two-panel figure of (A) $w$, and \Ho{} corner plot and (B)$H(z)$ for CE. We can include a posterior of $H(z=z_{\text{best measured}})$ as an inset to the $H(z)$ plot.}
    \label{fig:XG_corner}
    \script{XG_corner.py}
\end{figure}

>>>>

% Define document class
\documentclass[]{aastex631}
\usepackage{showyourwork}
\usepackage{macros}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{acro}
\acsetup{patch/longtable=false}

\DeclareAcronym{LVK}{short=LVK, long=LIGO Virgo KAGRA}
\DeclareAcronym{O5}{short=O5, long=the fifth LIGO Virgo KAGRA observing run}

@@

In other words, when using parametric models, $\frac{\diff N}{\diff t_{\det} \diff \theta_i} (\theta_i;\Lambda)$ in Equation~\ref{eq:inhomog-poisson} is calculated by evaluating a specific functional form described by a small set of hyper-parameters. 
With the GP approach, the hyper-parameters describing the mass distribution are the rate at each event-level posterior sample's source frame mass, and the rate at each found injection's source frame mass.
% The source frame mass is different for each possible value of \Ho{} and \Omm{}, so the hyper-parameters are defined in different locations for each draw from the hyper-posterior.
We therefore have $N_{\text{evs}}M + N_{\text{inj}}$ mass hyper-parameters, where $N_{\text{ev}}$ is the number of events, $M$ is the number of posterior samples per event, and $N_{\text{inj}}$ is the number of injections used to calculate the selection function $\xi$.
We label these $\{\mathcal{R}_{ij},\mathcal{R}_k\}$, and our full set of hyper-parameters is $\Lambda=\{H_0, \Omega_M, \mathcal{R}_{ij},\mathcal{R}_k\}$. 
In this way, our GP-based mass distribution is similar to the autoregressive population models used in ~\citet{callister_parameter-free_2023}.
Indeed, an autoregressive model is a Gaussian process with a particular choice of kernel.

@@

% \begin{figure}
%     \centering
%     \includegraphics[width=\textwidth]{figures/CE_GP.pdf}
%     \caption{Two-panel figure of (A) $w$, and \Ho{} corner plot and (B)$H(z)$ for CE. We can include a posterior of $H(z=z_{\text{best measured}})$ as an inset to the $H(z)$ plot.}
%     \label{fig:XG_corner}
%     \script{XG_corner.py}
% \end{figure}
